### 2025-04-25 multiple-regression.qmd
20250425 - reorganize

## Examples {#sec-multipleRegressionExamples}

### Predicting Wide Receivers' Fantasy Points {#sec-multipleRegressionFantasyPointsWRs}

@@

#### Examine Descriptive Statistics {#sec-multipleRegressionFantasyPointsWRsDescriptive}

@@

#### Examine Bivariate Associations {#sec-multipleRegressionFantasyPointsWRsBivariate}

@@

#### Estimate Multiple Regression Model {#sec-multipleRegressionFantasyPointsWRsModel}

@@

#### Evaluating and Addressing Assumptions {#sec-multipleRegressionExamplesAddressingAssumptions}

@@

##### Linear Association {#sec-multipleRegressionExamplesAddressingAssumptionsLinearAssociation}

@@

##### Homoscedasticity {#sec-multipleRegressionExamplesAddressingAssumptionsHomoscedasticity}

@@

##### Uncorrelated Residuals {#sec-multipleRegressionExamplesAddressingAssumptionsUncorrelatedResiduals}

@@

##### Normally Distributed Residuals {#sec-multipleRegressionExamplesAddressingAssumptionsNormallyDistributedResiduals}

>>>>

## Example: Predicting Wide Receivers' Fantasy Points {#sec-multipleRegressionFantasyPointsWRs}

@@

### Examine Descriptive Statistics {#sec-multipleRegressionFantasyPointsWRsDescriptive}

@@

### Examine Bivariate Associations {#sec-multipleRegressionFantasyPointsWRsBivariate}

@@

### Estimate Multiple Regression Model {#sec-multipleRegressionFantasyPointsWRsModel}

@@

### Evaluating and Addressing Assumptions {#sec-multipleRegressionExamplesAddressingAssumptions}

@@

#### Linear Association {#sec-multipleRegressionExamplesAddressingAssumptionsLinearAssociation}

@@

#### Homoscedasticity {#sec-multipleRegressionExamplesAddressingAssumptionsHomoscedasticity}

@@

#### Uncorrelated Residuals {#sec-multipleRegressionExamplesAddressingAssumptionsUncorrelatedResiduals}

@@

#### Normally Distributed Residuals {#sec-multipleRegressionExamplesAddressingAssumptionsNormallyDistributedResiduals}
